Rank verification for exponential families

### 2016-04-15 verifying-winner.tex
Comments added / addressed, color changed

\documentclass[11pt]{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{caption}
\usepackage{cleveref}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage[totalwidth=480pt, totalheight=680pt]{geometry}
\usepackage{mathrsfs}
\usepackage{tikz}
\usetikzlibrary{calc}
\usepackage{xcolor}

@@

%Commands for inline commenting that shows up on pdf
\newcommand{\WFcomment}[1]{{\color{red}{(WF: \bf \sc #1) }}}

@@

\item This has a hidden upward selection bias, or ``winner's curse'', as we are only testing this hypothesis as Trump is leading in the polls. In other words, the hypothesis itself is random. Alternatively, we can note that the marginal type I error rate is indeed not so straightforward. If the null hypothesis is ``$H_0: \text{Leader in polls has most support}$'', then for any distribution $F$ the marginal type I error rate is

@@

\item Comparing Trump to all other candidates involves multiple comparisons. Without considering the structure of this problem, common methods like Tukey's correction \cite{Tukey:1951} may largely decrease the test power.

@@

In this paper, we focus on Schur-concave exponential family, a broad class of distribution that is defined in \Cref{sec:exponential_families} and includes various examples listed in \Cref{sec:applications}. We constructed a selective level-$\alpha$ test for verifying that the largest observation is stochastically largest as well. The test provides selective type I error control, as well as enables us to construct confidence bound on the differences between the natural parameters and verify the order of the rest of natural parameters.

@@

Suppose we observe
$$\left(X_1, \ldots, X_n\right) \sim \text{Multinomial}\left(m, \pi\right)$$
and we want to test
$$H_{0j}: \pi_j \le \max_{k \ne j} \pi_k = \bigcup_{k \ne j} H_{0jk}: \pi_j \le \pi_k$$
when $X_j$ is larger than all other $X_k$. To break ties, we introduce independent auxiliary random variable $U_j \sim U\left[0,1\right]$, and opt to test $H_{0j}$ in the event of
$$A_j = \left\{X_j + U_j > \max_{k \ne j} X_k + U_k\right\}.$$
The distribution, written in an exponential family format, is
$$\exp\left(X_1 \log \pi_1 + \cdots + X_n \log \pi_n\right) \frac{1_{X_1 + \cdots + X_n = m}}{X_1! \cdots X_n!}.$$

Without loss of generality, we will assume $X_1$ is considered largest with the tie-breaking method above in mind. Following the construction in \cite{Fithian:2014ws}, if we want to construct $p$-values $p_{1j}$ for $H_{01j}$, we need to first re-parametrize such that the selection event $A_1$ can be expressed as the sufficient statistic. The distribution is now
$$\exp\left(\frac{X_1 - X_j}{2} \left(\log \pi_1 - \log \pi_j\right) + \cdots + \frac{X_1 + X_j}{2} \left(\log \pi_1 + \log \pi_j\right) + \cdots + X_n \log \pi_n\right) \frac{1_{X_1 + \cdots + X_n = m}}{X_1! \cdots X_n!}.$$

Next we condition on the sufficient statistics that are multiplied to the the nuisance parameter, in other words, we consider the conditional law
$$\mathcal{L}_{\pi_1 = \pi_j}\left(\frac{X_1 - X_j}{2} \middle| X_2, \ldots, \frac{X_1 + X_j}{2}, \ldots, X_n, A_1\right),$$
or equivalently, the conditional law
$$\mathcal{L}_{\pi_1 = \pi_j}\left(X_1 \middle| X_2, \ldots, \frac{X_1 + X_j}{2}, \ldots, X_n, A_1\right),$$
which is the distribution $\text{Binomial}\left(X_1 + X_j, \frac{1}{2}\right)$ truncated by the event $A_1$. The one-sided $p$-value $p_{1j}$ is thus given as
\begin{align*}
p_{ij}\left(x_1, \ldots, x_n\right) & = \PP\left(X_1 \ge x_1 \middle| X_2 = x_2, \ldots, \frac{X_1 + X_j}{2} = \frac{x_1 + x_j}{2}, \ldots, X_n = x_n, A_1\right) \\
& = \frac{\sum_{t = x_1}^{x_1 + x_j} \binom{x_1 + x_j}{t} \left(\frac{1}{2}\right)^{x_1 + x_j}}{\sum_{t = \left(x_1 + x_j\right)/2}^{x_1 + x_j} \binom{x_1 + x_j}{t} \left(\frac{1}{2}\right)^{x_1 + x_j}} \\
& = \frac{\sum_{t = x_1}^{x_1 + x_j} \binom{x_1 + x_j}{t}}{\sum_{t = \left(x_1 + x_j\right)/2}^{x_1 + x_j} \binom{x_1 + x_j}{t}},
\end{align*}
and to account for the tie-breaking we adopted earlier, we
\begin{itemize}
\item multiply the first term in the numerator and the denominator by $1/k$ where $k$ is the number of observations tied for largest; otherwise,
\item multiply the first term in the denominator by $1/2$ if $X_1$ and $X_2$ has the same parity.
\end{itemize}
Noticing that if there are ties for the largest the $p$-value is $1$ and the denominator is really $1/2$ otherwise, we can write
$$p_{1j} = 1 \wedge 2 \sum_{t=X_1}^{X_1 + X_j} \binom{X_i + X_j}{t}.$$

It is possible to check that $p_{12} \ge p_{1j}$ for any $j > 2$. Since the null hypothesis we are testing is a union of these smaller null hypothesis, the type I error rate is
$$\PP_{H_{01}}\left(p_{12} < \alpha \middle| A_1\right) \le \max_{j>1} \PP_{H_{01j}}\left(p_{12} < \alpha \middle| A_1\right) \le \max_{j>1} \PP_{H_{01j}}\left(p_{1j} < \alpha \middle| A_1\right) \le \alpha,$$
meaning that it is sufficient to construct a one-sided test between $X_1$ and $X_2$ and consider only $p_{12}$.

It may appear quite surprising that ``verifying a winner'' as we propose in this section requires no adjustment for multiplicity, in the sense that we only need to compare the winner to the runner- up, just as we would have done if $n = 2$. After all, we know that the winner suffer’s from a winner's curse: given $X_5$ is the winner, $X_5 / m$ would overestimate $\pi_5$, and the larger $n$ is, the more severe this bias is likely to be. However, if $X_9$ is the runner-up, then $X_9 / m$ is likely biased upward nearly as much as $X_5$. Informally, we might say that $X_9$ suffer’s from a “runner-up’s curse” that is nearly as bad as the winner's curse; as a result, $X_5 - X_9$ is actually not all that biased upward. By multiplying the $p$-value by $2$, or equivalently performing a two-tailed test, we take care of what little bias there is. Indeed, performing a two-tailed test can be viewed as a sort of ``correction for multiplicity'', albeit one that we would have to make even if $n = 2$.

@@

\Cref{fig:power} gives the power curves for $\text{Multinomial}\left(m, \pi\right)$ and
$$\pi \propto \left(e^\delta, 1, \ldots, 1\right),$$
for various combinations of $m$ and $n$. For Gupta and Nagel, we use $\alpha = 0.05$; but to account for the extra factor of $\frac{n-1}{n}$ in \Cref{eqn:selective_vs_marginal}, we will apply the selective procedure for with $\frac{n}{n-1} \alpha$ such that the marginal type I error rate such that both procedures are controlled at $\alpha$. Gupta and Nagel coincides with our test at $n = 2$; however as $n$ grows, the selective test shoes significantly more power than Gupta and Nagel's test.

@@

We would like to extend the result from multinomials to exponential families. We henceforth focus on exponential distribution taking the form
\begin{equation}
X \sim \exp\left(\theta_1 X_1 + \cdots + \theta_n X_n\right) g\left(X\right) h\left(\theta\right).
\label{eqn:exp_family}
\end{equation}
It is reasonable to assume that the family is ``symmetric'', i.e.\ if $\theta_j = \theta_k$, then the probability distribution remains the same when $X_j$ and $X_k$ are swapped. This corresponds to requiring $g\left(X\right)$ to be symmetric. We would also like to introduce a fairly mild additional condition that $g$ is {\em Schur-concave}. But first we recall the notion of {\em majorization}.

@@

\begin{figure}[htbp]
\begin{center}
\begin{tikzpicture}
	\coordinate (C1) at (60:5);
	\coordinate (C2) at (300:3);
	\coordinate (A) at (60:3);
	\coordinate (B) at ($(A) + (330:3)$);
	\draw[dashed] (0, 0) -- (C1);
	\draw[dashed] (0, 0) -- (C2);
	\fill[yellow!50] (0, 0) -- (C1) -- ($(C1) + (7, 0)$) -- ($(C2) + (8, 0)$) -- (C2) -- cycle;
	\node[above left] at ($(C2) + (8, 0)$) {$A_1$};
	\draw[thick] (A) -- (B) node[midway, above right] {$A$};
	\draw[thick, ->] (B) -- ++(330:5) node[midway, above right] {$B$};
	\fill (A) circle(2pt) node[above left] {$\left(M_{12}, M_{12}, X_3\right)$};
	\fill (B) circle(2pt) node[above right] {$\left(X_1, X_2, X_3\right)$};
	\draw[thick, ->] (0, 0) -- (1, 0) node[right] {\tiny $\left(1, 0, 0\right)$};
	\draw[thick, ->] (0, 0) -- (120:1) node[above] {\tiny $\left(0, 1, 0\right)$};
	\draw[thick, ->] (0, 0) -- (240:1) node[below] {\tiny $\left(0, 0, 1\right)$};
\end{tikzpicture}
\end{center}
\caption{The $p$-value $p_{12}$ can be written in terms of integral $A$ along the segment and $B$ along the ray. The diagram is drawn a level set of $x_1 + x_2 + x_3$. The yellow region represents the selection event $A_1$.}
\label{fig:p-value}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\begin{tikzpicture}
	\coordinate (C1) at (60:5);
	\coordinate (C2) at (300:3);
	\coordinate (A) at (60:3);
	\coordinate (B) at ($(A) + (330:3)$);
	\coordinate (C) at ($(0, 0)!(B)!(C2)$);
	\coordinate (D) at ($(A) + (150:1)$);
	\draw[dashed] (0, 0) -- (C1);
	\draw[dashed] (0, 0) -- (C2);
	\fill[yellow!50] (0, 0) -- (C1) -- ($(C1) + (7, 0)$) -- ($(C2) + (8, 0)$) -- (C2) -- cycle;
	\node[above left] at ($(C2) + (8, 0)$) {$A_1$};
	\draw[thick] (A) -- (B) node[midway, above right] {$A$};
	\draw[thick, ->] (B) -- ++(330:5) node[midway, below left] {$B$};
	\fill (A) circle(2pt) node[above right] {$\left(M_{12}, M_{12}, X_3\right)$};
	\fill (B) circle(2pt) node[right] {$\left(X_1, X_2, X_3\right)$};
	\draw[thick] (C) -- (B) node[midway, below right] {$C$};
	\node[below] at (C) {$\left(M_{13}, X_2, M_{13}\right)$};
	\draw[thick, ->] (B) -- ++(30:5) node[midway, above left] {$D$};
	\fill ($(0, 0)!(B)!(C2)$) circle(2pt);
	\draw[thick, dashed] (A) -- (D) node[midway, below left] {$\hat{A}$};
	\fill (D) circle(2pt) node[above] {$\left(M_{13}, X_2 + D_{13}, X_3\right)$};
	\draw[thick, dotted] (C) -- (D) node[midway, below, rotate=-90] {$\succeq$};
	\draw[thick, dotted] (A) -- ++(0, -3) node[midway, below, rotate=-90] {$\succeq$};
	\draw[thick, dotted] ($(B) + (30:4)$) -- ($(B) + (330:4)$) node[midway, below, rotate=-90] {$\succeq$};
\end{tikzpicture}
\end{center}
\caption{The $p$-value $p_{12}$ can be written in terms of integral $A$ along the segment and $B$ along the ray; and $p_{13}$ in terms of $C$ and $D$. $A'$ would refer to the sum of $A$ with the dashed line portion labeled as $\hat{A}$, formally explained in \Cref{eqn:int_extension}. The majorization relation is indicated by the dotted line.}
\label{fig:compare_rays}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\begin{tikzpicture}
	\coordinate (C1) at (60:5);
	\coordinate (C2) at (300:3);
	\coordinate (A) at (60:3);
	\coordinate (B) at ($(A) + (330:3)$);
	\coordinate (C) at ($(0, 0)!(B)!(C2)$);
	\coordinate (D) at ($(A) + (150:1)$);
	\coordinate (C3) at ($(B) + (330:5)$);
	\coordinate (C4) at ($(B) + (30:5)$);
	\coordinate (C5) at ($(C3)!(C1)!(C4)$);
	\coordinate (C6) at ($(C3)!(C2)!(C4)$);
	\draw[dashed] (0, 0) -- (C1);
	\draw[dashed] (0, 0) -- (C2);
	\draw[dashed] (C5) -- (C6) node[midway, above, rotate = -90] {Truncation for $X_j < X_{j-1}$};
	\fill[yellow!50] (0, 0) -- (C1) -- (C5) -- (C6) -- (C2) -- cycle;
	\node[above] at ($(C2)!0.7!(C6)$) {$A_1$};
	\draw[thick] (A) -- (B) node[midway, above right] {$A$};
	\draw[thick] (B) -- (C3) node[midway, below left] {$B$};
	\fill (C3) circle(2pt);
	\fill (A) circle(2pt) node[above right] {$\left(M_{12}, M_{12}, X_3\right)$};
	\fill (B) circle(2pt) node[right] {$\left(X_1, X_2, X_3\right)$};
	\draw[thick] (C) -- (B) node[midway, below right] {$C$};
	\node[below] at (C) {$\left(M_{13}, X_2, M_{13}\right)$};
	\draw[thick] (B) -- (C4) node[midway, above left] {$D$};
	\fill (C4) circle(2pt);
	\fill ($(0, 0)!(B)!(C2)$) circle(2pt);
	\draw[thick, dashed] (A) -- (D) node[midway, below left] {$\hat{A}$};
	\fill (D) circle(2pt) node[above] {$\left(M_{13}, X_2 + D_{13}, X_3\right)$};
	\draw[thick, dotted] (C) -- (D) node[midway, below, rotate=-90] {$\succeq$};
	\draw[thick, dotted] (A) -- ++(0, -3) node[midway, below, rotate=-90] {$\succeq$};
	\draw[thick, dotted] ($(B) + (30:4)$) -- ($(B) + (330:4)$) node[midway, below, rotate=-90] {$\succeq$};
\end{tikzpicture}
\end{center}
\caption{The two $p$-values constructed corresponds to taking integrals of $g$ along these segments, that lie on a level set of $x_j + x_{j+1} + x_k$. The dashed line corresponds to extension in \Cref{eqn:int_extension}. The dotted line on the far right is the truncation that enforces $X_j < X_{j-1}$.}
\label{fig:crop_rays}
\end{figure}

>>>>

\documentclass[11pt]{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{caption}
\usepackage{cleveref}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage[totalwidth=480pt, totalheight=680pt]{geometry}
\usepackage{mathrsfs}
\usepackage{tikz}
\usetikzlibrary{calc}
\usepackage{xcolor}
\definecolor{mid_green}{HTML}{99d8c9}

@@

% Commands for inline commenting that shows up on pdf
\newcommand{\WFcomment}[1]{{\color{red}{(WF: \bf \sc #1) }}}
\newcommand{\KHcomment}[1]{{\color{green!60!black}{(KH: \bf \sc #1) }}}

@@

\item This has a hidden upward selection bias, or ``winner's curse'', as we are only testing this hypothesis as Trump is leading in the polls. In other words, the hypothesis itself is random. Alternatively, we can note that the marginal type I error rate is indeed not so straightforward. Specifically, the null hypothesis is ``$H_0 \left(X\right): \text{Leader in polls has most support}$'', which is random and dependent on poll data $X$. Then for any distribution $F$ the marginal type I error rate is

@@

\item Comparing Trump to all other candidates involves multiple comparisons. Without considering the structure of this problem, common methods that perform multiple comparisons may largely decrease the test power.

@@

In this paper, we focus on Schur-concave exponential family, a broad class of distribution that is defined in \Cref{sec:exponential_families} and includes various examples listed in \Cref{sec:applications}. We constructed a selective level-$\alpha$ test for verifying that the largest observation is stochastically largest as well. The test provides selective type I error control, as well as enables us to construct confidence bound on the differences between the natural parameters and verify the order of the rest of the natural parameters. \WFcomment{Still feels a bit abstract when you discuss these goals here.} \KHcomment{What if we don't mention the side results at all?}

@@

Suppose we observe
$$\left(X_1, \ldots, X_n\right) \sim \text{Multinomial}\left(m, \pi\right)$$
and we want to test
$$H_{0j}: \pi_j \le \max_{k \ne j} \pi_k = \bigcup_{k \ne j} H_{0jk}: \pi_j \le \pi_k$$
when $X_j$ is larger than all other $X_k$. In case of ties, we break them independently and randomly. The distribution, written in an exponential family format, is
$$\exp\left(X_1 \log \pi_1 + \cdots + X_n \log \pi_n\right) \frac{1_{X_1 + \cdots + X_n = m}}{X_1! \cdots X_n!}.$$

Without loss of generality, we will assume $X_1$ is considered largest with the tie-breaking method above in mind. Following the construction in \cite{Fithian:2014ws}, if we want to construct $p$-values $p_{1j}$ for $H_{01j}$, we need to first re-parametrize such that the selection event $A_1$ can be expressed in terms of the sufficient statistic. The distribution is now
$$\exp\left(\frac{X_1 - X_j}{2} \left(\log \pi_1 - \log \pi_j\right) + \cdots + \frac{X_1 + X_j}{2} \left(\log \pi_1 + \log \pi_j\right) + \cdots + X_n \log \pi_n\right) \frac{1_{X_1 + \cdots + X_n = m}}{X_1! \cdots X_n!}.$$

Next we condition on the sufficient statistics that are multiplied to the the nuisance parameter, in other words, we consider the conditional law
$$\mathcal{L}_{\pi_1 = \pi_j}\left(\frac{X_1 - X_j}{2} \middle| X_2, \ldots, \frac{X_1 + X_j}{2}, \ldots, X_n, A_1\right),$$
or equivalently, the conditional law
$$\mathcal{L}_{\pi_1 = \pi_j}\left(X_1 \middle| X_2, \ldots, \frac{X_1 + X_j}{2}, \ldots, X_n, A_1\right),$$
which is the distribution $\text{Binomial}\left(X_1 + X_j, \frac{1}{2}\right)$ truncated by the event $A_1$. The one-sided $p$-value $p_{1j}$ is thus given as
\begin{align*}
p_{ij}\left(x_1, \ldots, x_n\right) & = \PP\left(X_1 \ge x_1 \middle| X_2 = x_2, \ldots, \frac{X_1 + X_j}{2} = \frac{x_1 + x_j}{2}, \ldots, X_n = x_n, A_1\right) \\
& = \frac{\sum_{t = x_1}^{x_1 + x_j} \binom{x_1 + x_j}{t} \left(\frac{1}{2}\right)^{x_1 + x_j}}{\sum_{t = \left(x_1 + x_j\right)/2}^{x_1 + x_j} \binom{x_1 + x_j}{t} \left(\frac{1}{2}\right)^{x_1 + x_j}} \\
& = \frac{\sum_{t = x_1}^{x_1 + x_j} \binom{x_1 + x_j}{t}}{\sum_{t = \left(x_1 + x_j\right)/2}^{x_1 + x_j} \binom{x_1 + x_j}{t}},
\end{align*}
and to account for the tie-breaking we adopted earlier, we
\begin{itemize}
\item multiply the first term in the numerator and the denominator by $1/k$ where $k$ is the number of observations tied for largest; otherwise,
\item multiply the first term in the denominator by $1/2$ if $X_1$ and $X_j$ has the same parity, as the sum starts $X_1 = X_j = \frac{x_1 + x_j}{2}$.
\end{itemize}
Noticing that if $X_1, \ldots, X_j$ all tied the $p$-value is $1$, and the denominator is really $1/2$ otherwise \WFcomment{I don't think that's true for $j \neq 2$, is it?} \KHcomment{The denominator should always be half of a binomial distribution I think}, we can write
$$p_{1j} = 1 \wedge 2 \sum_{t=X_1}^{X_1 + X_j} \binom{X_i + X_j}{t}.$$

It is possible to check that $p_{12} \ge p_{1j}$ for any $j > 2$. The type I error rate is
$$\PP_{H_{01}}\left(p_{12} < \alpha \middle| A_1\right) \stackrel{\text{(i)}}{=} \max_{j>1} \PP_{H_{01j}}\left(p_{12} < \alpha \middle| A_1\right) \stackrel{\text{(ii)}}{\le} \max_{j>1} \PP_{H_{01j}}\left(p_{1j} < \alpha \middle| A_1\right) \stackrel{\text{(iii)}}{\le} \alpha,$$
where (i) follows from $H_{01} = \bigcup_{j>1} H_{01j}$; (ii) is true as $p_{12} \ge p_{1j}$ as long as $X_1 \ge X_2 \ge \max_{j>2} X_j$, which is guaranteed here as we conditioned on $A_1$; (iii) follows from the construction of $p_{1j}$. \KHcomment{I think the probability in the middle (between (i) and (ii)) is well-defined, as $p_{12}$ is just a random variable dependent on $X$.} Thus it is sufficient to construct a one-sided test between $X_1$ and $X_2$ and consider only $p_{12}$.

It may appear quite surprising that ``verifying a winner'' as we propose in this section requires no adjustment for multiplicity, in the sense that we only need to compare the winner to the runner-up, just as we would have done if $n = 2$. When $n=2$, the observation $X_1$ follows Binomial$\left(X_1 + X_2, \frac{1}{2}\right)$, coinciding with the test we proposed. After all, we know that the winner suffer’s from a winner's curse: given $X_5$ is the winner, $X_5 / m$ would overestimate $\pi_5$, and the larger $n$ is, the more severe this bias is likely to be. However, if $X_9$ is the runner-up, then $X_9 / m$ is likely biased upward nearly as much as $X_5$. Informally, we might say that $X_9$ suffer’s from a “runner-up’s curse” that is nearly as bad as the winner's curse; as a result, $X_5 - X_9$ is actually not all that biased upward. By multiplying the $p$-value by $2$, or equivalently performing a two-tailed test, we take care of what little bias there is. Indeed, performing a two-tailed test can be viewed as a sort of ``correction for multiplicity'', albeit one that we would have to make even if $n = 2$.

@@

\Cref{fig:power} gives the power curves for $\text{Multinomial}\left(m, \pi\right)$ and
$$\pi \propto \left(e^\delta, 1, \ldots, 1\right),$$
for various combinations of $m$ and $n$. For Gupta and Nagel, we use $\alpha = 0.05$; but to account for the extra factor of $\frac{n-1}{n}$ in \Cref{eqn:selective_vs_marginal}, we will apply the selective procedure for with $\frac{n}{n-1} \alpha$ such that the marginal type I error rate of both procedures are controlled at $\alpha$. \WFcomment{Can we justify this? Our procedure has error $\alpha$ in the case where all $\pi_j$ are equal.} \KHcomment{The selective error rate is $\alpha$, but Gupta and Nagel really only had marginal error rate. If all $\pi_j$ are equal, the marginal error rate is $\frac{n-1}{n} \alpha$.} Gupta and Nagel coincides with our test at $n = 2$; however as $n$ grows, the selective test shoes significantly more power than Gupta and Nagel's test.

@@

We would like to extend the result from multinomials to exponential families. We henceforth focus on exponential distribution taking the form
\begin{equation}
X \sim \exp\left(\theta_1 X_1 + \cdots + \theta_n X_n\right) g\left(X\right) h\left(\theta\right),
\label{eqn:exp_family}
\end{equation}
defined on the Lebesgue or counting measure. It is reasonable to assume that the family is ``symmetric'', i.e.\ if $\theta_j = \theta_k$, then the probability distribution remains the same when $X_j$ and $X_k$ are swapped. This corresponds to requiring $g\left(X\right)$ to be symmetric. We would also like to introduce a fairly mild additional condition that $g$ is {\em Schur-concave}. But first we recall the notion of {\em majorization}, defined on both $\mathbb{R}^n$ and $\mathbb{Z}^n$. \WFcomment{I think we're implicitly assuming here  that $g$ is a density wrt one of (a) Lebesgue or (b) counting measure. Is that right? And if so, do we need a couple sentences to explain why it works in the counting measure case? That is, we need the atoms of non-zero measure to match up with each other along the rays of interest, right?} \KHcomment{I think we are making that assumption. Added a few more words there but not sure if it is explicit enough.}

@@

\begin{figure}[htbp]
\begin{center}
\begin{tikzpicture}
	\coordinate (C1) at (60:5);
	\coordinate (C2) at (300:3);
	\coordinate (A) at (60:3);
	\coordinate (B) at ($(A) + (330:3)$);
	\draw[dashed] (0, 0) -- (C1);
	\draw[dashed] (0, 0) -- (C2);
	\fill[mid_green] (0, 0) -- (C1) -- ($(C1) + (7, 0)$) -- ($(C2) + (8, 0)$) -- (C2) -- cycle;
	\node[above left] at ($(C2) + (8, 0)$) {$A_1$};
	\draw[thick] (A) -- (B) node[midway, above right] {$A$};
	\draw[thick, ->] (B) -- ++(330:5) node[midway, above right] {$B$};
	\fill (A) circle(2pt) node[above left] {$\left(M_{12}, M_{12}, X_3\right)$};
	\fill (B) circle(2pt) node[above right] {$\left(X_1, X_2, X_3\right)$};
	\draw[thick, ->] (0, 0) -- (1, 0) node[right] {\tiny $\left(1, 0, 0\right)$};
	\draw[thick, ->] (0, 0) -- (120:1) node[above] {\tiny $\left(0, 1, 0\right)$};
	\draw[thick, ->] (0, 0) -- (240:1) node[below] {\tiny $\left(0, 0, 1\right)$};
\end{tikzpicture}
\end{center}
\caption{The $p$-value $p_{12}$ can be written in terms of integral $A$ along the segment and $B$ along the ray. The diagram is drawn a level set of $x_1 + x_2 + x_3$. The green region represents the selection event $A_1$.}
\label{fig:p-value}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\begin{tikzpicture}
	\coordinate (C1) at (60:5);
	\coordinate (C2) at (300:3);
	\coordinate (A) at (60:3);
	\coordinate (B) at ($(A) + (330:3)$);
	\coordinate (C) at ($(0, 0)!(B)!(C2)$);
	\coordinate (D) at ($(A) + (150:1)$);
	\draw[dashed] (0, 0) -- (C1);
	\draw[dashed] (0, 0) -- (C2);
	\fill[mid_green] (0, 0) -- (C1) -- ($(C1) + (7, 0)$) -- ($(C2) + (8, 0)$) -- (C2) -- cycle;
	\node[above left] at ($(C2) + (8, 0)$) {$A_1$};
	\draw[thick] (A) -- (B) node[midway, above right] {$A$};
	\draw[thick, ->] (B) -- ++(330:5) node[midway, below left] {$B$};
	\fill (A) circle(2pt) node[above right] {$\left(M_{12}, M_{12}, X_3\right)$};
	\fill (B) circle(2pt) node[right] {$\left(X_1, X_2, X_3\right)$};
	\draw[thick] (C) -- (B) node[midway, below right] {$C$};
	\node[below] at (C) {$\left(M_{13}, X_2, M_{13}\right)$};
	\draw[thick, ->] (B) -- ++(30:5) node[midway, above left] {$D$};
	\fill ($(0, 0)!(B)!(C2)$) circle(2pt);
	\draw[thick, dashed] (A) -- (D) node[midway, below left] {$\hat{A}$};
	\fill (D) circle(2pt) node[above] {$\left(M_{13}, X_2 + D_{13}, X_3\right)$};
	\draw[thick, dotted] (C) -- (D) node[midway, below, rotate=-90] {$\succeq$};
	\draw[thick, dotted] (A) -- ++(0, -3) node[midway, below, rotate=-90] {$\succeq$};
	\draw[thick, dotted] ($(B) + (30:4)$) -- ($(B) + (330:4)$) node[midway, below, rotate=-90] {$\succeq$};
\end{tikzpicture}
\end{center}
\caption{The $p$-value $p_{12}$ can be written in terms of integral $A$ along the segment and $B$ along the ray; and $p_{13}$ in terms of $C$ and $D$. $A'$ would refer to the sum of $A$ with the dashed line portion labeled as $\hat{A}$, formally explained in \Cref{eqn:int_extension}. The majorization relation is indicated by the dotted line.}
\label{fig:compare_rays}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\begin{tikzpicture}
	\coordinate (C1) at (60:5);
	\coordinate (C2) at (300:3);
	\coordinate (A) at (60:3);
	\coordinate (B) at ($(A) + (330:3)$);
	\coordinate (C) at ($(0, 0)!(B)!(C2)$);
	\coordinate (D) at ($(A) + (150:1)$);
	\coordinate (C3) at ($(B) + (330:5)$);
	\coordinate (C4) at ($(B) + (30:5)$);
	\coordinate (C5) at ($(C3)!(C1)!(C4)$);
	\coordinate (C6) at ($(C3)!(C2)!(C4)$);
	\draw[dashed] (0, 0) -- (C1);
	\draw[dashed] (0, 0) -- (C2);
	\draw[dashed] (C5) -- (C6) node[midway, above, rotate = -90] {Truncation for $X_j < X_{j-1}$};
	\fill[mid_green] (0, 0) -- (C1) -- (C5) -- (C6) -- (C2) -- cycle;
	\node[above] at ($(C2)!0.7!(C6)$) {$A_1$};
	\draw[thick] (A) -- (B) node[midway, above right] {$A$};
	\draw[thick] (B) -- (C3) node[midway, below left] {$B$};
	\fill (C3) circle(2pt);
	\fill (A) circle(2pt) node[above right] {$\left(M_{12}, M_{12}, X_3\right)$};
	\fill (B) circle(2pt) node[right] {$\left(X_1, X_2, X_3\right)$};
	\draw[thick] (C) -- (B) node[midway, below right] {$C$};
	\node[below] at (C) {$\left(M_{13}, X_2, M_{13}\right)$};
	\draw[thick] (B) -- (C4) node[midway, above left] {$D$};
	\fill (C4) circle(2pt);
	\fill ($(0, 0)!(B)!(C2)$) circle(2pt);
	\draw[thick, dashed] (A) -- (D) node[midway, below left] {$\hat{A}$};
	\fill (D) circle(2pt) node[above] {$\left(M_{13}, X_2 + D_{13}, X_3\right)$};
	\draw[thick, dotted] (C) -- (D) node[midway, below, rotate=-90] {$\succeq$};
	\draw[thick, dotted] (A) -- ++(0, -3) node[midway, below, rotate=-90] {$\succeq$};
	\draw[thick, dotted] ($(B) + (30:4)$) -- ($(B) + (330:4)$) node[midway, below, rotate=-90] {$\succeq$};
\end{tikzpicture}
\end{center}
\caption{The two $p$-values constructed corresponds to taking integrals of $g$ along these segments, that lie on a level set of $x_j + x_{j+1} + x_k$. The dashed line corresponds to extension in \Cref{eqn:int_extension}. The dotted line on the far right is the truncation that enforces $X_j < X_{j-1}$.}
\label{fig:crop_rays}
\end{figure}
